\section{Chapter 3}

\subsection{Example}

Warning: localisation might not produce a local ring, for example see \href{https://math.stackexchange.com/questions/628371/a-f-is-not-a-local-ring}{HERE}.

If we localise at a prime ideal $\mathfrak p$ then it's local. See \href{https://math.stackexchange.com/questions/300446/why-is-the-localization-at-a-prime-ideal-a-local-ring#:~:text=Well%2C%20any%20proper%20ideal%20m,p%20is%20a%20local%20ring.}{HERE}.

\subsection{Proposition 3.7}

Localisation commutes with tensor product. See \href{http://sporadic.stanford.edu/math210a/sol4.pdf}{HERE} for a pure tensor manipulation. See \href{https://math.stackexchange.com/questions/2292960/localization-commutes-with-tensor-products}{HERE} for a post, using universal property of tensor product.

\subsection{Proposition 3.11}

For i), I have some doubts in the last step of \href{https://math.stackexchange.com/questions/375353/every-ideal-of-the-localization-is-an-extended-ideal}{HERE}.

For iv), in the proof we have \textit{"$S^{-1}A/S^{-1}\mathfrak p\simeq \overline{S}^{-1}(A/\mathfrak p)$"}. In fact we if we apply exact functor $S^{-1}(-)$ to first isomorphism exact sequence we'll get it, with $S^{-1}$ but not $\overline{S}^{-1}$???

See a post discussing this \href{https://math.stackexchange.com/questions/1630232/localization-commutes-with-quotient}{HERE}. In the second answer, it used Universal Property of Localisation to prove the isomorphism...

For v), about extension of ideal, which really should be discussed in Chap 1.
\href{https://math.stackexchange.com/questions/367073/about-the-definition-of-extended-ideals}{HERE} is a post, discussion the definition.

For a more detailed treatment, see The Rising Sea 1.3.F. EXERCISE.

\subsection{Proposition 3.14}

One might wonder if the condition of finitely-generated is omitted what will happen?

Let $A=k[x]$ where $k$ is a field, and define 
$$M=\bigoplus_{i=2}^{\infty}\frac{k[x]}{x^i}=\frac{k[x]}{x^2}\oplus \frac{k[x]}{x^3}\oplus\cdots.$$

It's not finitely-generated as $k[x]-$module. 

Let $S=\{1,x,x^2,...\}$.

Notice that by definition $S^{-1}M=0$ given that for any $m\in M$ we can always choose a large enough $s\in S$ such that $sm=0$.

On the other hand we have $\operatorname{Ann}(M)=0$, which gives us
$$0=S^{-1}(\operatorname{Ann}(M))\neq \operatorname{Ann}(S^{-1}M)=\operatorname{Ann}(0)=k[x]$$

\subsection{Proposition 3.16} 

Question on the last equality. Purely based on the contents we knew $$\mathfrak q^c \supset \mathfrak p^{ec}=\mathfrak p.$$

Denote the ring homomorphism from $A\to B$ as $f$.
Conversely, we proceed by a contrapositive arguement. Suppose we have $x\in \mathfrak q^c\setminus \mathfrak p$, then $f(x)\in \mathfrak q$ and $f(x)\in f(A-\mathfrak p)=S$ by definition. But it was ensured that $\mathfrak q\cap S=\emptyset$, contradiction.

\subsection{Side Notes}

There are some examples from Reid's Undergraduate C.A, see P41. 

\subsection{Ex 1.}

$\Leftarrow:$ Assume the existence of an element $s\in S$ such that $sM=0$. For any element $m_0/s_0\in S^{-1}M$, we claim 
$$m_0/s_0=0/1 ~\text{ given }~ s(m_0\cdot 1 - s_0\cdot 0)=sm_0=0.$$Since every element is zero, hence $S^{-1}M=0$. 

$\Rightarrow:$ Since $M$ is finitely-generated, let $m_1,...,m_n$ be its generators for some $n\in\mathbb Z$. For each $m_i$, there's some $s_i\in S$ such that 
$s_im_i=0$ by assumption. Now we define 
$$s=\prod_{i=1}^n s_i$$ and claim that $sM=0$. 
This because for any $m\in M$, we can express it as $a_1m_1+\cdots+ a_nm_n=m\in M$ for some coefficients $a_i\in A$. Furthermore, we notice \begin{align*}
    sm =& s(a_1m_1+\cdots+ a_nm_n)
       = a_1sm_1+\cdots a_nsm_n=0,
\end{align*}which proves $sM=0$.

\ding{45} "finitely-generated $A$-module $M$" is important? Any counterexample???


\subsection{Ex 2.}

We recall the charactersation of Jacobson radical in a ring. For any element $x\in \operatorname{Jac}()$

\subsection{Ex 3.}

% https://q.uiver.app/#q=WzAsNCxbMCwwLCJBICJdLFsxLDAsIlNeey0xfUEiXSxbMiwwLCJVXnstMX0oU157LTF9QSkiXSxbMSwxLCIoU1QpXnstMX1BIl0sWzAsMywiZ18xIiwyXSxbMCwxLCJmXzEiXSxbMSwyLCJmXzIiXSxbMSwzLCJmXzMiLDJdLFsyLDMsIlxcZXhpc3RzICEgXFxwaGkiLDIseyJjdXJ2ZSI6MSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzMsMiwiXFxleGlzdHMgISBcXHBzaSIsMix7ImN1cnZlIjoxLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
\[\begin{tikzcd}
	{A } & {S^{-1}A} & {U^{-1}(S^{-1}A)} \\
	& {(ST)^{-1}A}
	\arrow["{g_1}"', from=1-1, to=2-2]
	\arrow["{f_1}", from=1-1, to=1-2]
	\arrow["{f_2}", from=1-2, to=1-3]
	\arrow["{f_3}"', from=1-2, to=2-2]
	\arrow["{\exists ! \phi}"', curve={height=6pt}, dashed, from=1-3, to=2-2]
	\arrow["{\exists ! \psi}"', curve={height=6pt}, dashed, from=2-2, to=1-3]
\end{tikzcd}\]

Firstly, we claim that $f_2\circ f_1$ will send every element of $ST$ to a unit in $U^{-1}(S^{-1}A)$. Hence by universal property there's a unique map 
$$\psi:(ST)^{-1}A\to U^{-1}(S^{-1}A).$$

Proof for the first claim. Element of $ST$ is like $st$ for some $s\in S$ and $t\in T$. Under $f_1$, $s/1$ is a unit in $S^{-1}A$ and $t/1\in U$. Furthermore, under $f_2$, element $f_2(t/1)$ will be a unit in $U^{-1}(S^{-1}A)$. And we have $f_2\circ f_1(st)=\frac{st/1}{1}$ is a unit for there exists \begin{align*}
    \frac{1/s}{t/1}\in U^{-1}(S^{-1}A) ~\text{ such that }~ \frac{st/1}{1}\cdot\frac{1/s}{t/1}=1.
\end{align*}

Secondly, we claim that $f_3$ will send every element of $U$ to unit in $(ST)^{-1}A$, which give rise to the unique existence of 
$$\phi:U^{-1}(S^{-1}A)\to (ST)^{-1}A.$$

Proof for the second claim. Note that the map 
$$f_3: S^{-1}A\to (ST)^{-1}A$$ is a ring inclusion. Clearly $t/1\in U$ will be a unit under $f_3$ in $(ST)^{-1}A$ given $1/t\in (ST)^{-1}A$ and $t/1\cdot 1/t=1$.

Both maps are unique and making the diagram commute, hence they're isomorphisms.


See Stack Project Prop 10.9.10 \href{https://stacks.math.columbia.edu/tag/00CM}{HERE}. See this page, for a discussion between isomorphisms of localisations as either ring or module...

\subsection{Ex 4.}

My approach was to produce two unique morphisms by universal property of $S^{-1}B$ and $T^{-1}B$, respectively. 

% https://q.uiver.app/#q=WzAsMyxbMCwxLCJCIl0sWzEsMCwiU157LTF9QiJdLFsxLDIsIlReey0xfUIiXSxbMCwxLCJiXFxtYXBzdG8gYi8xIl0sWzAsMiwiYlxcbWFwc3RvIGIvZigxKSIsMl0sWzEsMiwiXFxleGlzdHMhIiwyLHsiY3VydmUiOjEsInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6ImRhc2hlZCJ9fX1dLFsyLDEsIlxcZXhpc3RzICEiLDIseyJjdXJ2ZSI6MSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV1d
\[\begin{tikzcd}
	& {S^{-1}B} \\
	B \\
	& {T^{-1}B}
	\arrow["{b\mapsto b/1}", from=2-1, to=1-2]
	\arrow["{b\mapsto b/f(1)}"', from=2-1, to=3-2]
	\arrow["{\exists!}"', curve={height=6pt}, dashed, from=1-2, to=3-2]
	\arrow["{\exists !}"', curve={height=6pt}, dashed, from=3-2, to=1-2]
\end{tikzcd}\]

But it seems to be difficult to write in valid proof....

See a post discuss a more straight-forward approach \href{https://math.stackexchange.com/questions/375454/s-1b-and-t-1b-isomorphic-for-t-fs}{HERE}, and \href{https://math.stackexchange.com/questions/1459441/fa-to-b-ring-homomorphism-s-multiplicatively-closed-subset-of-a-what-does}{HERE}. In the first post, there's an obvious map to define and module homomorphism together with surjectivity easy to check. For the injectivity, we can check... 

\subsection{Ex 5.}

I encountered a problem, wishing to prove $x/1\neq 0/1$ in the localised ring.


\textit{A potentially incorrect solution}

We wish to prove that 
$$\operatorname{Nil}(A)=\bigcap_{\mathfrak p\in\operatorname{Spec}A}\mathfrak p=0.$$

For the localised ring $A_{\mathfrak p}$, by Prop 3.11 (i) and Coro 3.13, we know every ideals are extended ideals and 
\begin{align*}
	0=\operatorname{Nil}(A_{\mathfrak p}) =& \bigcap_{\mathfrak q\in\operatorname{Spec}A,~ \mathfrak q\subset \mathfrak p} \mathfrak q^{e}\supset \left(\bigcap_{\mathfrak q\in\operatorname{Spec}A,~ \mathfrak q\subset \mathfrak p} \mathfrak q\right)^e
\end{align*}where the last inclusion is given by Exercise 1.18 on Page 10 of Atiyah's textbook. But the only way that an extended ideal to be zero is the ideal 
$$\bigcap_{\mathfrak q\in\operatorname{Spec}A,~ \mathfrak q\subset \mathfrak p} \mathfrak q=0.$$ Therefore we have 
\begin{align*}
	\operatorname{Nil}(A) =& \bigcap_{\mathfrak p\in\operatorname{Spec}A}\mathfrak p\subset \bigcap_{\mathfrak q\in\operatorname{Spec}A,~ \mathfrak q\subset \mathfrak p} \mathfrak q=0.
\end{align*}

See a post \href{https://math.stackexchange.com/questions/2095939/proof-check-being-reduced-is-a-local-property-atiyah-macdonald-3-5?rq=1}{HERE}. For examples...

See a post \href{https://math.stackexchange.com/questions/2095939/proof-check-being-reduced-is-a-local-property-atiyah-macdonald-3-5?rq=1}{HERE}. It used Corollary 3.12.

\textit{"Being an integral domain is not a local property."} See a post \href{https://math.stackexchange.com/questions/685844/is-being-an-integral-domain-a-local-property}{HERE}.

Possible counterexamples including $\mathbb Z/6\mathbb Z$, $\mathbb C[x,y]/\langle xy\rangle$, etc. 
But I'm not sure about the what will be the localisation... 
One very simple way to construct a counterexample to take product of two integral domains. 
Say $R=\mathbb Q\times\mathbb Q$. According to Milne's Notes on Algebraic Number Theory Page 15, "Ideals in product of rings", we know that prime ideals in $R$ is of the form $\mathfrak q=\mathfrak p\times \mathbb Q$ or $\mathbb Q\times\mathfrak p$ where $\mathfrak p\subset\mathbb Q$ is a prime ideal. We can see that $R_{\mathfrak q}$ is always an integral domain. However, $R$ is not an integral domain for $(1,0),(0,1)$ are nontrivial zero-divisors.

\subsection{Ex 6.}

Apply Zorn's Lemma. Since $A\neq 0$, hence it has identity. Then $\{1\}$ would be a multiplicatively closed subset. Hence $\sum$ is nonempty. Each \textit{chain} is bounded above by $A\setminus\{\text{zerodivisors}\}$. \ding{54}!!!
This is a wrong way to apply Zorn. Because I was confused how to find the correct upper bound!!\\

The set $\sum$ is nonempty and ordered by inclusion as illustrated above. Fix a chain, the upper bound is the union of all multiplicatively close subsets \[M=\bigcup S_i\] where $S_i$ are all multiplicatively closed subsets in the chain. Clearly, union of multiplicatively closed subsets $M$ is again multiplicatively closed and crutially we know $0\notin M$. Therefore each chain is bounded above, then we can apply Zorn's Lemma to conclude the existence of a maximal element $M_0\in \sum$.